\documentclass[20pt]{article}

\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{graphicx}

\title{Trip-Tracker App}
\author{Victoria Mendoza}
\date{June 22, 2017}

\begin{document}
	\begin{titlepage}
		\maketitle 
		\tableofcontents
	\end{titlepage}

	\section{Global Significance} %\par
		\hspace*{.25 in}
		 %Navigation, more user friendly w features to entertain ppl, goal guide, inform, and entertain (goal)
		 The overall global significance of this app is to provide users with a \textbf{user-friendly} application that not only provides navigation but also attracts users with entertainment. The main goal is to \textbf{guide, inform, and entertain} users all in one app used for travel.
	\section{Personal Project Importance}
		%first challenges to create app all by myself
		%suggested by a teacher
		\hspace{.25 in}
		This project is significant for me because it would be the first app I will ever create with self-driven motivation. I will try to use the least amount of help as possible, however, I know there are many mentors available if anything becomes complicated to solve. \\\par
		Another factor that is significant to me is that this project idea was suggested to me by my computer science teacher a while back. She had advised me to attempt to create an app on my own, and now I would like to accomplish that. 
	\section{Learning Outcome}
	%paragraph: more java stuff and how to operate Backendless
		\hspace*{.25 in}Once I complete this project, I hope to have learned more about how to use the programs \textbf{Android Studio} and \textbf{Backendless}. I've practiced with Android Studio this past school year, however; I would like to continue learning how to use it. There are many features I have yet to learn on it along with more Java functions to assimilate as well.\\\par
		Although I've never used the Backendless before, I am determined to successfully learn and use it for my application. I've heard of its functions through research and it seems as a manageable program to learn within two to three weeks. I look forward in becoming more comfortable with using these programs through this project.
		
	\section{Project Objectives}
	%what you want to accomplish; successfully use Backendless for the first time
		\hspace{.25 in}This project may be time consuming, mainly because I'm not a master at programming, however; the main objective for this project is to have a somewhat developed app by the due date of this project. Even if I don't finish within these three weeks, I plan on attempting to finish this app on my own time.\newline - Another major goal is to successfully understand and use Backendless for my first time.
		
	\section{Project Timeline}
	%description list??
		\begin{tabular}{c|c}
			\textbf{Week 1} & Have at least 80 percent of my project outline done on Android Studio\\ \\
			\hline
			\textbf{Week 2} & Have design of the app done on Android Studio along with functional operations.\\ \\
			\hline
			\textbf{Week 3} & Have Backendless working with my app and have at least 80 percent of the app complete\\ \\	
		\end{tabular}
	
	\section{Helpful Mentors}
		\subsection*{Here at UTEP}
			\begin{itemize}
				\item \textbf{Dr. Ceberio}\\
				\item \textbf{Joseph}\\
				\item \textbf{Jesus}\\
				\item \textbf{Leo}\\
				\item \textbf{Angel}\\
			\end{itemize}
		\subsection*{Other Mentors}
			\begin{itemize}
				\item \underline{Mrs. Robles} (Computer Science teacher from Eastlake High School)
				\item \underline{Mr. Coles} (Computer Science teacher from Eastlake High School)
			\end{itemize}
		
	\section{Inspirational Projects}
	%list? w/ description
		\begin{description}
			\item \emph{- WAZE}: The entertainment aspects of this application is what attracts users.
			\item \emph{- Google Maps}: A very popular app that provides navigational information which is very useful for users.
		\end{description}
\end{document}